Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description

### 2020-11-18 paper/main.tex
restructure quotes aPPA vs pPPA

%
\citep{baumann2016functional} paradigm: We measure parahippocampal responses
while participants engaged in a task that required them to judge the contextual
relatedness of scene and object pairs, which were presented either as words or
pictures \citep{baumann2016functional}.
%
Participants judged the contextual relatedness of scene and object pairs (“bike”
\& “bell” are a contextually congruent object– object pair, “sofa” \&
“microscope” are incongruent; “boat” \& “lake” are a contextually congruent
object–scene pair, “tractor” \& “hotel” are
incongruent)\citep{baumann2016functional}.
%
Each pair was presented either in printed-word format or in a combined
word–picture format. That allowed us to present pictorial objects and scenes in
isolation (Fig. 1)\citep{baumann2016functional}.
%
To identify visuospatial regions of the PHC, we tested for voxels with greater
activity for picture–scene trials than for picture–object trials over and above
activity differences elicited by the comparison of word–scene trials and word–
object trials\citep{baumann2016functional}.
%
Additionally to locate context-related regions of the PHC, we tested for voxels
that were selectively active during the contextual judgment task regardless of
the type of stimulus (scenes vs objects) or presentation modality (word vs
picture)\citep{baumann2016functional}.

>>>>

%
\citep{baumann2016functional} paradigm: We measure PHC responses while
participants engaged in a task that required them to judge the contextual
relatedness of scene and object pairs, which were presented either as words or
pictures \citep{baumann2016functional}.
%
Participants judged the contextual relatedness of scene and object pairs (“bike”
\& “bell” are a contextually congruent object– object pair, “sofa” \&
“microscope” are incongruent; “boat” \& “lake” are a contextually congruent
object–scene pair, “tractor” \& “hotel” are
incongruent)\citep{baumann2016functional}.
%
Each pair was presented either in printed-word format or in a combined
word–picture format. That allowed us to present pictorial objects and scenes in
isolation (Fig. 1)\citep{baumann2016functional}.
%
To identify visuospatial regions of the PHC, we tested for voxels with greater
activity for picture–scene trials than for picture–object trials over and above
activity differences elicited by the comparison of word–scene trials and word–
object trials\citep{baumann2016functional}.
%
Additionally to locate context-related regions of the PHC, we tested for voxels
that were selectively active during the contextual judgment task regardless of
the type of stimulus (scenes vs objects) or presentation modality (word vs
picture)\citep{baumann2016functional}.
